ManuscriptPURFits

### 2024-01-23 Code/ManuscriptPURFits.Rmd
Fixed .Rmd to run - needs more edits

# MyWavelengths = c(450, 530, 660, "WW")
# MCMIXColours = c(w_length2rgb(450), w_length2rgb(530), w_length2rgb(660), "black")
library(photobiology)

MyWavelengths = c("WW", 660, 530, 450)
# MCMIXColours = c("black", w_length2rgb(660), w_length2rgb(530),  w_length2rgb(450))
MCMIXColours = c("black", "orange", w_length2rgb(530),  w_length2rgb(450))

@@

DummyDF_SS120 <- expand_grid(
  Dummy_Strain, Dummy_Photoperiod, Dummy_Par_ue, Dummy_O2_uM, Dummy_WL, Dummy_deltaOD_Lmu_corr, Dummy_Pur_ue, Dummy_deltaOD_Lmu_corr_day,Dummy_PUR_day
  ) %>%
  mutate(ID = "DummySS120")

@@

DummyDF_MIT9313 <- expand_grid(
  Dummy_Strain, Dummy_Photoperiod, Dummy_Par_ue, Dummy_O2_uM, Dummy_WL, Dummy_deltaOD_Lmu_corr, Dummy_Pur_ue, Dummy_deltaOD_Lmu_corr_day,Dummy_PUR_day
  ) %>%
  mutate(ID = "DummyMIT9313")

@@

DummyDF_MED4 <- expand_grid(
  Dummy_Strain, Dummy_Photoperiod, Dummy_Par_ue, Dummy_O2_uM, Dummy_WL, Dummy_deltaOD_Lmu_corr, Dummy_Pur_ue, Dummy_deltaOD_Lmu_corr_day,Dummy_PUR_day
  ) %>%
  mutate(ID = "DummyMED4")

@@

```{r add dummy dark growth to DF}

@@

```{r test MED4 issues}
# PURPARFits |>
#   filter(Strain == "MED4",
#          O2_uM == 250) |>
#   select(c(ReplicateMean_deltaOD_Lmu_corr_day,  OrgPur_day))
```

```{r set colours}

# MyWavelengths = c(450, 530, 660, "WW")
# MCMIXColours = c(w_length2rgb(450), w_length2rgb(530), w_length2rgb(660), "black")
# 
# MyWavelengths = c("WW", 660, 530, 450)
# MCMIXColours = c("black", w_length2rgb(660), w_length2rgb(530),  w_length2rgb(450))
# 
# names(MCMIXColours) <- MyWavelengths
# MCMIXColours
# 
# 
# 
# 
# ColoursStrain = c(MIT9313 = "#E69F00", SS120 = "#F0E442", MED4 = "#CC79A7" )
# 
# MyOxygen = c(2.5, 25, 250 )
# # ColourOxygen = c("#99CCFF", "dodgerblue", "blue1")
# ColourOxygen = c("#FFCC00", "#FF9900", "#663300")
# names(ColourOxygen) <- MyOxygen
# ColourOxygen
# 
# MyOxygen = c(2.5, 25, 250 )
# LineTypeOxygen = c("dotted", "longdash", "solid")
# names(LineTypeOxygen) <- MyOxygen
# LineTypeOxygen
# 
# MyPhotoperiods = as.factor(c(4, 8, 12, 16))
# ColoursPhotoperiod = c("gray88", "lightcyan3", "gray47", "gray8")
# names(ColoursPhotoperiod) <- MyPhotoperiods
# ColoursPhotoperiod

```{r set shapes}

# MyPhotoperiods = as.factor(c(4, 8, 12, 16))
# PhotoperiodShapes = c(6, 18, 1, 17)
# 
# 
# names(PhotoperiodShapes) <- MyPhotoperiods
# PhotoperiodShapes
# 
# O2Shapes <- c(13, 1, 19)

Set Strip colors for WL x_strip is for WL facetted by columns and y_strip is for WL faceted by rows
```{r}
# x_strip <- strip_themed(background_x = elem_list_rect(fill = MCMIXColours, alpha = 0.8),
#                       background_y = elem_list_rect(fill = "grey27")) 
# 
# x_stripWW <- strip_themed(background_x = elem_list_rect(fill = "black"),
#                       background_y = elem_list_rect(fill = "#grey27"))
# 
# x_strip660 <- strip_themed(background_x = elem_list_rect(fill = "#730000"),
#                       background_y = elem_list_rect(fill = "#grey27"))
# 
# x_strip530 <- strip_themed(background_x = elem_list_rect(fill = "#00FF00"),
#                       background_y = elem_list_rect(fill = "#grey27"))
# 
# x_strip450 <- strip_themed(background_x = elem_list_rect(fill = "#0600FF"),
#                       background_y = elem_list_rect(fill = "#grey27"))
# 
# y_strip <- strip_themed(background_y = elem_list_rect(fill = MCMIXColours),
#                       background_x = elem_list_rect(fill = "#grey27")) 
# 
# y_stripWW <- strip_themed(background_y = elem_list_rect(fill = "black"),
#                       background_x = elem_list_rect(fill = "#grey27"))
# 
# y_strip660 <- strip_themed(background_y = elem_list_rect(fill = "#730000"),
#                       background_x = elem_list_rect(fill = "#grey27"))
# 
# y_strip530 <- strip_themed(background_y = elem_list_rect(fill = "#00FF00"),
#                       background_x = elem_list_rect(fill = "#grey27"))
# 
# y_strip450 <- strip_themed(background_y = elem_list_rect(fill = "#0600FF"),
#                       background_x = elem_list_rect(fill = "#grey27"))

@@

# mm <- function(I, KM, Pmax){(Pmax* I)/(KM + I)}
# 
# plot(x = TestI, y = mm(I = TestI, KM = 10, Pmax = 1))

# mmsubi <- function(I, KM, Pmax, Ki){(Pmax* I)/(KM + (I * (1 + I/Ki)))}
# 
# plot(x = TestI, y = mmsubi(I = TestI, KM = 10, Pmax = 1, Ki = 1))

@@

# model with dummy dark, 0 PAR,  growth rates. Also removed data if no growth occurred under an O2 and photoperiod condition so that the model would not be skewed towards zero. As per Amanda and Doug's advice, filtered out PUR d-1 above 1.5e+06 because only photoperiods greater than 4 hrs have PUR d-1 above.
PURPARStrainO2NestDummy_filtered <- PURPARFits_dummy |>
  mutate(remove = case_when(Strain == "MED4" & Photoperiod == 4 ~ 1,
                            Strain == "MED4" & O2_uM == 25 & Photoperiod == 8 & WL == "WW" ~ 1,
                            Strain == "MIT9313" & O2_uM == 2.5 & Photoperiod == 16 ~ 1,
                            Strain == "MIT9313" & O2_uM == 2.5 & Photoperiod == 12 & WL == "WW" ~ 1,
                            Strain == "SS120"  & O2_uM == 2.5 & Photoperiod %in% c(16,8,4) ~ 1,
                            Strain == "SS120"  & O2_uM == 25 & Photoperiod %in% c(16) & WL == 450 ~ 1,
                            Strain == "SS120"  & O2_uM == 250 & Photoperiod %in% c(4) & WL == 450 ~ 1,
                            TRUE ~ 0)) |>
   filter(remove == 0,
          PURPhotonDose_day <= 1.5e+06) |>
  nest(data = -c("Strain","O2_uM")) |>
  # mutate(GRC_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grc(I = PURPhotonDose_day, a, Pmax),
  #                             data = .x,
  #                             start = list(a = 1e-6,
  #                                          Pmax = 1),
  #                             lower = c(0, 0),
  #                             upper = c(1,100)
  #                        ), NULL)
  #                        )
  #        ) |>
  # mutate(GRC_Param = map(GRC_Model, tidy),
  #        GRC_Predict = map(GRC_Model, possibly(augment), NULL),
  #        GRC_Glance = map(GRC_Model, possibly(glance))) |>
  mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
                              data = .x,
                              start = list(a = 1e-7, b = 1e-8, Pmax = 1), 
                              lower = c(0, 0, 0),
                              upper = c(1,1,100)
                         ), 0)
                         )
         ) |>
  mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
         GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
         GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
         ) |>
  mutate(GRClm_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ LinEqn(x = PURPhotonDose_day,  M, Intercept),
                              data = .x,
                              start = LinEqnStart
                         ), NULL)
                         )
         ) |>
  mutate(GRClm_Param = map(GRClm_Model, tidy),
         GRClm_Predict = map(GRClm_Model, possibly(augment)),
         GRClm_Glance = map(GRClm_Model, possibly(glance))
         )

PURPARStrainO2NestDummy <- PURPARFits_dummy |>
  nest(data = -c("Strain","O2_uM")) |>
  # mutate(GRC_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grc(I = PURPhotonDose_day, a, Pmax),
  #                             data = .x,
  #                             start = list(a = 1e-6,
  #                                          Pmax = 1),
  #                             lower = c(0, 0),
  #                             upper = c(1,100)
  #                        ), NULL)
  #                        )
  #        ) |>
  # mutate(GRC_Param = map(GRC_Model, tidy),
  #        GRC_Predict = map(GRC_Model, possibly(augment), NULL),
  #        GRC_Glance = map(GRC_Model, possibly(glance))) |>
  mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
                              data = .x,
                              start = list(a = 1e-7, b = 1e-8, Pmax = 1), 
                              lower = c(0, 0, 0),
                              upper = c(1,1,100)
                         ), 0)
                         )
         ) |>
  mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
         GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
         GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
         ) |>
  mutate(GRClm_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ LinEqn(x = PURPhotonDose_day,  M, Intercept),
                              data = .x,
                              start = LinEqnStart
                         ), NULL)
                         )
         ) |>
  mutate(GRClm_Param = map(GRClm_Model, tidy),
         GRClm_Predict = map(GRClm_Model, possibly(augment)),
         GRClm_Glance = map(GRClm_Model, possibly(glance))
         )

# PURPARStrainO2NestDummy_TEST <- PURPARFits_dummy |>
#   nest(data = -c("Strain","O2_uM")) |>
# mutate(GRC_Model_Photoperiod = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day * Photoperiod ~ grc(I = PURPhotonDose_day, a, Pmax),
#                             data = .x,
#                             start = list(a = 1e-6,
#                                          Pmax = 1),
#                             lower = c(0, 0),
#                             upper = c(1,100)
#                        ), NULL)
#                        )
#        ) |>
# mutate(GRC_Param_Photoperiod = map(GRC_Model_Photoperiod, tidy),
#        GRC_Predict_Photoperiod = map(GRC_Model_Photoperiod, possibly(augment), NULL),
#        GRC_Glance_Photoperiod = map(GRC_Model_Photoperiod, possibly(glance))) |>
#   mutate(GRCplatt_Model_Photoperiod = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day * Photoperiod ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
#                               data = .x,
#                               start = list(a = 1e-7, b = 1e-8, Pmax = 1),
#                               lower = c(0, 0, 0),
#                               upper = c(1,1,100)
#                          ), NULL)
#                          )
#          ) |>
#   mutate(GRCplatt_Param_Photoperiod = map(GRCplatt_Model_Photoperiod, tidy),
#          GRCplatt_Predict_Photoperiod = map(GRCplatt_Model_Photoperiod, possibly(augment)),
#          GRCplatt_Glance_Photoperiod = map(GRCplatt_Model_Photoperiod, possibly(glance))
#          ) %>%
#     mutate(GRC_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grc(I = PURPhotonDose_day, a, Pmax),
#                               data = .x,
#                               start = list(a = 1e-6,
#                                            Pmax = 1),
#                               lower = c(0, 0),
#                               upper = c(1,100)
#                          ), NULL)
#                          )
#          ) |>
#   mutate(GRC_Param = map(GRC_Model, tidy),
#          GRC_Predict = map(GRC_Model, possibly(augment), NULL),
#          GRC_Glance = map(GRC_Model, possibly(glance))) |>
#   mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
#                               data = .x,
#                               start = list(a = 1e-7, b = 1e-8, Pmax = 1),
#                               lower = c(0, 0, 0),
#                               upper = c(1,1,100)
#                          ), NULL)
#                          )
#          ) |>
#   mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
#          GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
#          GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
#          )
# 
# PURPARStrainO2NestDummy_TEST

# PURPARStrainO2PhotoperiodNest <- PURPARFits |>
#   nest(data = -c("Strain","O2_uM", "Photoperiod")) |>
#   mutate(GRC_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grc(I = PURPhotonDose_day, a, Pmax),
#                               data = .x,
#                               start = list(a = 1e-6,
#                                            Pmax = 1),
#                               lower = c(0, 0),
#                               upper = c(1,100)
#                          ), NULL)
#                          )
#          ) |>
#   mutate(GRC_Param = map(GRC_Model, possibly(tidy)),
#          GRC_Predict = map(GRC_Model, possibly(augment), NULL),
#          GRC_Glance = map(GRC_Model, possibly(glance))) |>
#   mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
#                               data = .x,
#                               start = list(a = 1e-7, b = 1e-8, Pmax = 1),
#                               lower = c(0, 0, 0),
#                               upper = c(1,1,100)
#                          ), NULL)
#                          )
#          ) |>
#   mutate(GRCplatt_Param = map(GRCplatt_Model, possibly(tidy)),
#          GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
#          GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
#          )

# model with dummy dark, 0 PAR, 0 growth rates
#Note: fit fails for SS120, 12h photoperiod and O2 = 25uM. Works if I remove outlier(WL = 660 and PAR = 30 or MiSa1456) 
PURPARStrainO2PhotoperiodNestDummy <- PURPARFits_dummy |>
   filter(ID != "MiSa1456") %>% 
   # filter(ID != "JuNa1068") %>% 
 nest(data = -c("Strain","O2_uM", "Photoperiod")) |>
  # mutate(GRC_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grc(I = PURPhotonDose_day, a, Pmax),
  #                             data = .x,
  #                             start = list(a = 1e-6,
  #                                          Pmax = 1),
  #                             lower = c(0, 0),
  #                             upper = c(1,100)
  #                        ), NULL)
  #                        )
  #        ) |>
  # mutate(GRC_Param = map(GRC_Model, tidy),
  #        GRC_Predict = map(GRC_Model, possibly(augment), NULL),
  #        GRC_Glance = map(GRC_Model, possibly(glance))) |>
  mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
                              data = .x,
                              start = list(a = 1e-8, b = 1e-9, Pmax = 1),
                              lower = c(-0, 0, 0),
                              upper = c(1,1,100)
                         ), NULL)
                         )
         ) |>
  mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
         GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
         GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
         ) |>
  mutate(GRClm_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ LinEqn(x = PURPhotonDose_day,  M, Intercept),
                              data = .x,
                              start = LinEqnStart
                         ), NULL)
                         )
         ) |>
  mutate(GRClm_Param = map(GRClm_Model, tidy),
         GRClm_Predict = map(GRClm_Model, possibly(augment)),
         GRClm_Glance = map(GRClm_Model, possibly(glance))
         )

# model with dummy dark, 0 PAR,  growth rates
PURPARStrainO2WLNestDummy <- PURPARFits_dummy |>
  nest(data = -c("Strain","O2_uM", "WL")) |>
  # mutate(GRC_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grc(I = PURPhotonDose_day, a, Pmax),
  #                             data = .x,
  #                             start = list(a = 1e-6,
  #                                          Pmax = 1),
  #                             lower = c(0, 0),
  #                             upper = c(1,100)
  #                        ), 0)
  #                        )
  #        ) |>
  # mutate(GRC_Param = map(GRC_Model, tidy),
  #        GRC_Predict = map(GRC_Model, possibly(augment), NULL),
  #        GRC_Glance = map(GRC_Model, possibly(glance))) |>
  mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
                              data = .x,
                              start = list(a = 1e-7, b = 1e-8, Pmax = 1),
                              lower = c(0, 0, 0),
                              upper = c(1,1,100)
                         ), 0)
                         )
         ) |>
  mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
         GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
         GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
         )|>
  mutate(GRClm_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ LinEqn(x = PURPhotonDose_day,  M, Intercept),
                              data = .x,
                              start = LinEqnStart
                         ), NULL)
                         )
         ) |>
  mutate(GRClm_Param = map(GRClm_Model, tidy),
         GRClm_Predict = map(GRClm_Model, possibly(augment)),
         GRClm_Glance = map(GRClm_Model, possibly(glance))
         )

# model with dummy dark, 0 PAR,  growth rates
PURPARStrainO2PeriodWLNestDummy <- PURPARFits_dummy |>
  nest(data = -c("Strain","O2_uM", "Photoperiod", "WL")) |>
  # mutate(GRC_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grc(I = PURPhotonDose_day, a, Pmax),
  #                             data = .x,
  #                             start = list(a = 1e-6,
  #                                          Pmax = 1),
  #                             lower = c(0, 0),
  #                             upper = c(1,100)
  #                        ), 0)
  #                        )
  #        ) |>
  # mutate(GRC_Param = map(GRC_Model, tidy),
  #        GRC_Predict = map(GRC_Model, possibly(augment), NULL),
  #        GRC_Glance = map(GRC_Model, possibly(glance), )) |>
  mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
                              data = .x,
                              start = list(a = 1e-7, b = 1e-8, Pmax = 1),
                              lower = c(0, 0, 0),
                              upper = c(1,1,100)
                         ), 0)
                         )
         ) |>
  mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
         GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
         GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
         )|>
  mutate(GRClm_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ LinEqn(x = PURPhotonDose_day,  M, Intercept),
                              data = .x,
                              start = LinEqnStart
                         ), NULL)
                         )
         ) |>
  mutate(GRClm_Param = map(GRClm_Model, tidy),
         GRClm_Predict = map(GRClm_Model, possibly(augment)),
         GRClm_Glance = map(GRClm_Model, possibly(glance))
         )

@@

PURPARStrainO2BestModelsDummy <- PURPARStrainO2NestDummy|>
  # select(-c(data)) |>
  pivot_longer(cols = -c(Strain, O2_uM, data)) |>
  drop_na(value) |>
  filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param")) |>
  separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
  pivot_wider(names_from = Output, values_from = value) |>
   # filter(!map_lgl(Model, is.null)) |>
  filter(!map_lgl(Glance, is.null)) |>
  mutate(AIC = map_dbl(Glance, possibly(~ as.numeric(pluck(.x, "AIC"))))) |>
  group_by(Strain, O2_uM) |>
  filter(AIC == min(AIC)) |>
  ungroup() |>
  select(-c(Model, Glance)) |>
  unnest(Param) |>
  select(-c(statistic)) |>
  pivot_wider(names_from = term, values_from = c(estimate, std.error, p.value))

@@

PURPARStrainO2BestModelsDummy_filtered <- PURPARStrainO2NestDummy_filtered|>
  # select(-c(data)) |>
  pivot_longer(cols = -c(Strain, O2_uM, data)) |>
  drop_na(value) |>
  filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param")) |>
  separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
  pivot_wider(names_from = Output, values_from = value) |>
   # filter(!map_lgl(Model, is.null)) |>
  filter(!map_lgl(Glance, is.null)) |>
  mutate(AIC = map_dbl(Glance, possibly(~ as.numeric(pluck(.x, "AIC"))))) |>
  group_by(Strain, O2_uM) |>
  filter(AIC == min(AIC)) |>
  ungroup() |>
  select(-c(Model, Glance)) |>
  unnest(Param) |>
  select(-c(statistic)) |>
  pivot_wider(names_from = term, values_from = c(estimate, std.error, p.value))

>>>>

library(photobiology)

MyWavelengths = c("WW", 660, 530, 450)
MCMIXColours = c("black", w_length2rgb(660), w_length2rgb(530),  w_length2rgb(450))

@@

DummyDF_SS120 <- expand_grid(
  Dummy_Strain, Dummy_Photoperiod, Dummy_Par_ue, Dummy_O2_uM, Dummy_WL, Dummy_deltaOD_Lmu_corr, Dummy_Pur_ue, Dummy_deltaOD_Lmu_corr_day,Dummy_PUR_day
  ) %>%
  mutate(SampleID = "DummySS120")

@@

DummyDF_MIT9313 <- expand_grid(
  Dummy_Strain, Dummy_Photoperiod, Dummy_Par_ue, Dummy_O2_uM, Dummy_WL, Dummy_deltaOD_Lmu_corr, Dummy_Pur_ue, Dummy_deltaOD_Lmu_corr_day,Dummy_PUR_day
  ) %>%
  mutate(SampleID = "DummyMIT9313")

@@

DummyDF_MED4 <- expand_grid(
  Dummy_Strain, Dummy_Photoperiod, Dummy_Par_ue, Dummy_O2_uM, Dummy_WL, Dummy_deltaOD_Lmu_corr, Dummy_Pur_ue, Dummy_deltaOD_Lmu_corr_day,Dummy_PUR_day
  ) %>%
  mutate(SampleID = "DummyMED4")

@@

# Join dummy df to growth df
```{r add dummy dark growth to DF}

@@

@@

@@

# model with dummy dark, 0 PAR,  growth rates. Also removed data if no growth occurred for an O2 and photoperiod combination so that the model including all photoperiods would not be skewed towards zero. As per Amanda and Doug's advice, filtered out PUR d-1 above 1.5e+06 because only photoperiods greater than 4 hrs have PUR d-1 above.
PURPARStrainO2NestDummy_filtered <- PURPARFits_dummy |>
  mutate(remove = case_when(Strain == "MED4" & Photoperiod == 4 ~ 1,
                            Strain == "MED4" & O2_uM == 25 & Photoperiod == 8 & WL == "WW" ~ 1,
                            Strain == "MIT9313" & O2_uM == 2.5 & Photoperiod == 16 ~ 1,
                            Strain == "MIT9313" & O2_uM == 2.5 & Photoperiod == 12 & WL == "WW" ~ 1,
                            Strain == "SS120"  & O2_uM == 2.5 & Photoperiod %in% c(16,8,4) ~ 1,
                            Strain == "SS120"  & O2_uM == 25 & Photoperiod %in% c(16) & WL == 450 ~ 1,
                            Strain == "SS120"  & O2_uM == 250 & Photoperiod %in% c(4) & WL == 450 ~ 1,
                            TRUE ~ 0)) |>
   filter(remove == 0,
          PURPhotonDose_day <= 1.5e+06) |>
  nest(data = -c("Strain","O2_uM")) |>
  mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
                              data = .x,
                              start = list(a = 1e-7, b = 1e-8, Pmax = 1), 
                              lower = c(0, 0, 0),
                              upper = c(1,1,100),
                              control = list(maxiter = 500)
                         ), NULL)
                         )
         ) |>
  mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
         GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
         GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
         ) |>
  mutate(GRClm_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ LinEqn(x = PURPhotonDose_day,  M, Intercept),
                              data = .x,
                              start = LinEqnStart
                         ), NULL)
                         )
         ) |>
  mutate(GRClm_Param = map(GRClm_Model, tidy),
         GRClm_Predict = map(GRClm_Model, possibly(augment)),
         GRClm_Glance = map(GRClm_Model, possibly(glance))
         )

PURPARStrainO2NestDummy <- PURPARFits_dummy |>
  nest(data = -c("Strain","O2_uM")) |>
  mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
                              data = .x,
                              start = list(a = 1e-7, b = 1e-8, Pmax = 1), 
                              lower = c(0, 0, 0),
                              upper = c(1,1,100),
                              control = list(maxiter = 500)
                         ), NULL)
                         )
         ) |>
  mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
         GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
         GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
         ) |>
  mutate(GRClm_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ LinEqn(x = PURPhotonDose_day,  M, Intercept),
                              data = .x,
                              start = LinEqnStart
                         ), NULL)
                         )
         ) |>
  mutate(GRClm_Param = map(GRClm_Model, tidy),
         GRClm_Predict = map(GRClm_Model, possibly(augment)),
         GRClm_Glance = map(GRClm_Model, possibly(glance))
         )

# model with dummy dark, 0 PAR, 0 growth rates
#Note: fit fails for SS120, 12h photoperiod and O2 = 25uM. Works if I remove outlier(WL = 660 and PAR = 30 or MiSa1456) 
PURPARStrainO2PhotoperiodNestDummy <- PURPARFits_dummy |>
   filter(SampleID != "MiSa1456") %>% 
   # filter(SampleID != "JuNa1068") %>% 
 nest(data = -c("Strain","O2_uM", "Photoperiod")) |>
  mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
                              data = .x,
                              start = list(a = 1e-8, b = 1e-9, Pmax = 1),
                              lower = c(-0, 0, 0),
                              upper = c(1,1,100),
                              control = list(maxiter = 500)
                         ), NULL)
                         )
         ) |>
  mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
         GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
         GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
         ) |>
  mutate(GRClm_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ LinEqn(x = PURPhotonDose_day,  M, Intercept),
                              data = .x,
                              start = LinEqnStart
                         ), NULL)
                         )
         ) |>
  mutate(GRClm_Param = map(GRClm_Model, tidy),
         GRClm_Predict = map(GRClm_Model, possibly(augment)),
         GRClm_Glance = map(GRClm_Model, possibly(glance))
         )

# model with dummy dark, 0 PAR,  growth rates
PURPARStrainO2WLNestDummy <- PURPARFits_dummy |>
  nest(data = -c("Strain","O2_uM", "WL")) |>
  mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
                              data = .x,
                              start = list(a = 1e-7, b = 1e-8, Pmax = 1),
                              lower = c(0, 0, 0),
                              upper = c(1,1,100),
                              control = list(maxiter = 500)
                         ), NULL)
                         )
         ) |>
  mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
         GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
         GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
         )|>
  mutate(GRClm_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ LinEqn(x = PURPhotonDose_day,  M, Intercept),
                              data = .x,
                              start = LinEqnStart
                         ), NULL)
                         )
         ) |>
  mutate(GRClm_Param = map(GRClm_Model, tidy),
         GRClm_Predict = map(GRClm_Model, possibly(augment)),
         GRClm_Glance = map(GRClm_Model, possibly(glance))
         )

# model with dummy dark, 0 PAR,  growth rates
PURPARStrainO2PeriodWLNestDummy <- PURPARFits_dummy |>
  nest(data = -c("Strain","O2_uM", "Photoperiod", "WL")) |>
  mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
                              data = .x,
                              start = list(a = 1e-7, b = 1e-8, Pmax = 1),
                              lower = c(0, 0, 0),
                              upper = c(1,1,100),
                              control = list(maxiter = 500)
                         ), NULL)
                         )
         ) |>
  mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
         GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
         GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
         )|>
  mutate(GRClm_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ LinEqn(x = PURPhotonDose_day,  M, Intercept),
                              data = .x,
                              start = LinEqnStart
                         ), NULL)
                         )
         ) |>
  mutate(GRClm_Param = map(GRClm_Model, tidy),
         GRClm_Predict = map(GRClm_Model, possibly(augment)),
         GRClm_Glance = map(GRClm_Model, possibly(glance))
         )

@@

PURPARStrainO2BestModelsDummy <- PURPARStrainO2NestDummy|>
  # select(-c(data)) |>
  pivot_longer(cols = -c(Strain, O2_uM, data)) |>
  drop_na(value) |>
  filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param")) |>
  separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
  pivot_wider(names_from = Output, values_from = value) |>
  filter(!map_lgl(Model, is.null)) |>
  filter(!map_lgl(Glance, is.null)) |>
  mutate(AIC = map_dbl(Glance, possibly(~ as.numeric(pluck(.x, "AIC"))))) |>
  group_by(Strain, O2_uM) |>
  filter(AIC == min(AIC)) |>
  ungroup() |>
  select(-c(Model, Glance)) |>
  unnest(Param) |>
  select(-c(statistic)) |>
  pivot_wider(names_from = term, values_from = c(estimate, std.error, p.value))

@@

PURPARStrainO2BestModelsDummy_filtered <- PURPARStrainO2NestDummy_filtered|>
  # select(-c(data)) |>
  pivot_longer(cols = -c(Strain, O2_uM, data)) |>
  drop_na(value) |>
  filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param")) |>
  separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
  pivot_wider(names_from = Output, values_from = value) |>
    filter(!map_lgl(Model, is.null)) |>
  filter(!map_lgl(Glance, is.null)) |>
  mutate(AIC = map_dbl(Glance, possibly(~ as.numeric(pluck(.x, "AIC"))))) |>
  group_by(Strain, O2_uM) |>
  filter(AIC == min(AIC)) |>
  ungroup() |>
  select(-c(Model, Glance)) |>
  unnest(Param) |>
  select(-c(statistic)) |>
  pivot_wider(names_from = term, values_from = c(estimate, std.error, p.value))
